GRASS GIS Vector state of the art\\ Gearing towards GRASS GIS 7

### 2013-10-09 grassposter/2014_EGU_G7_Landscape/poster.tex
First changes to the poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@57965 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{GRASS GIS image processing environment\\ Gearing towards GRASS GIS 7}
\author{Yann Chemin\\
International Water Management Institute}

@@

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Multi- and hyperspectral data analysis}{
\smallskip
Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
that ideally come from a land cover that is covering at least one full pixel in the image
studied.

>>>>

\title{GRASS GIS Vector state of the art\\ Gearing towards GRASS GIS 7}
\author{Markus Neteler, ...\\
GRASS GIS Development Team}

@@

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Multi- and hyperspectral data analysis}{
\smallskip
Unmixing of mixed pixels (i.spec.unmix [9]) is based on the identification of original
spectral signatures that are ideally derived from land covers that cover at least one
full pixel in the image (pure endmembers).
